\documentclass[a4paper,twoside,onecolumn,openright]{memoir}

\setlrmarginsandblock{2.5cm}{2.5cm}{*}
\setulmarginsandblock{2.5cm}{2.5cm}{*}
\checkandfixthelayout

\copypagestyle{thesis}{ruled}
\makeevenfoot{thesis}{}{}{\thepage} % Align right page number on even footer
\makeoddfoot{thesis}{}{}{\thepage}  % Align right page number on odd footer
\pagestyle{thesis}

\chapterstyle{veelo}

\usepackage{prelude/lhs2TeX}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Ghengin: A type-heavy, shader-centric Haskell game engine}
\author{Rodrigo Mesquita}

\begin{document}

\maketitle

\chapter{Ghengin}

\begin{itemize}
  \item A render packet definition that validates the mesh and material of the
    render packet across the render pipeline it will be rendered in.
  \item Pattern matching on existential materials through type reps
  \item Most serious games should think about how their game is rendered. ...be
      dissatisfied with the general purpose solutions which might never feel
        ``just right''
  \item There's usually a big jump of unknown from the materials defined in the
      editor and properties defined to the code written. The code should be
        more tighly coupled to the rest of the game (in terms of things that
        directly influence e.g. rendering), in which things are more explicit
        and foundational. We use types for this. See Core.
\end{itemize}

\section{Core}

Ghengin is defined by its Core.
Ghengin should have a small Core that we can reason about.
Every other feature (e.g. light) should be readily desugared to Core.
By understanding Core, one can understand the whole of Ghengin more easily, and figure out the differences between more advanced features.

Identify Ghengin Core and thoroughly specify it.

Currently I see Core as
\begin{itemize}
    \item Render pipelines with render properties
    \item Materials which are a group of properties that define the surface
        things
    \item Meshes, which are vertices defined by a group of vertex properties,
        and also mesh properties which are per-mesh properties.
    \item Properties themselves (Floats, Vec3s, Texture2Ds + Samplers are a
        possible instance)? Or should the properties be the same for all
        "Cores"? I think the properties being an abstract ``X'' which can be
        instanced X = any group of properties. I quite like Ghengin(X) in the
        style of OutsideIn(X) or HM(X).
\end{itemize}

\begin{itemize}
    \item Lights are just syntactic sugar for render pipeline properties.
    \item Material albedos, textures, normal maps, are just material properties.
    \item Transforms and per-mesh colors are just mesh properties.
    \item We can understand all features because they map to the same much
        simpler Core. There's no hard ambiguity in features between different
        light types, or material types, or anything, and it's all connected and
        enforced in the code written through the types.
\end{itemize}



\section{Render Pipeline}

\section{Meshes}

\section{Materials}

A \textbf{Material} is usually regarded as a core component of a rendering
engine which describes surface properties that define the visual appearence of
meshes when rendered. Material properties can include the surface color,
texture, parameters of lighting such as specularity, or custom parameters for a
custom shader.

We define a Material as a collection of properties that each \emph{render
packet} has. This collection of properties is passed to the shader programs
every frame and will ultimately define how each render packet is rendered. In
contrast to existing material systems, ...

\section{Render Packets}

% TODO: Render keys for pipelines are TypeReps ;)

\section{Entity Component System\label{sec:ecs}}



\include{ocean/Tutorial.tex}

\end{document}

